---
title: "Small Countries are beautiful"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(plotly)
library(knitr)
knitr::opts_chunk$set(echo = F)
source("Chart#2.R")
```

#Summary 

```{r}
raw <- read.csv("data/WDVP Datasets - small countries are beautiful.csv", stringsAsFactors = FALSE)
data_set <- raw[5:76, ]

```
Even though varies in shapes and sizes, small nations are showing fascinating trends and discoveries for investigation. In this [dataset](https://docs.google.com/spreadsheets/d/11LhOlwsloUuA495r-04IDwciMqNrLwWGpveqpF61WXU/edit#gid=1246185258), we analyzed the dataset from the _76 countries_ about their economic situation, life standards and also population distribution. 



#Chart 1: Foreign immigrants analysis



#Chart 2: Health expenditure analysis
For the second chart, we analyzed the relationship between the *health expenditure* and the *human development index* for 2017 in the 76 countries. The country name and the value of human development index, the health expenditure would be shown by clicking on the bar interested. 

```{r}
data_set <- read.csv("data/WDVP Datasets - small countries are beautiful.csv", stringsAsFactors = FALSE, na.strings = "-")

chart_two <- get_second_chart(data_set)
chart_two

```