---
title: "Small Countries are beautiful"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(plotly)
library(knitr)
library(lintr)
knitr::opts_chunk$set(echo = F)
source("analysis.R")
source("Chart#1.R")
source("Chart#2.R")
```

Even though varies in shapes and sizes, small nations are showing fascinating trends and discoveries for investigation. In this [dataset](https://docs.google.com/spreadsheets/d/11LhOlwsloUuA495r-04IDwciMqNrLwWGpveqpF61WXU/edit#gid=1246185258), we analyzed the dataset from the _76 countries_ about their economic situation, life standards and also population distribution. 

#Summary 

```{r}
small_countries_df <- read.csv(
  "data/WDVP Datasets - small countries are beautiful.csv",
  stringsAsFactors = F, na.strings = "-")

small_countries_df <- small_countries_df[5:nrow(small_countries_df), ]
list_max_min <- summarize_information(small_countries_df)
options("scipen"=100, "digits"=4)
```
In this dataset, we find the maximum and minimum and also the average for the analysis that is given for the dataset. 

1. `r list_max_min$population$max$indicator[1]` , `r list_max_min$population$max$indicator[2]` and `r list_max_min$population$max$indicator[3]` have the biggest population among the 76 countries, which is `r list_max_min$population$max$population[1]`. `r list_max_min$population$min$indicator[1]`, `r list_max_min$population$min$indicator[2]`, `r list_max_min$population$min$indicator[3]`, `r list_max_min$population$min$indicator[4]`, `r list_max_min$population$min$indicator[5]` and `r list_max_min$population$min$indicator[6]` have the smallest population, which is `r list_max_min$population$min$population[1]`. The average population among the countries is `r list_max_min$population$avg`. 

2. `r list_max_min$GDP$max$indicator[1]` has the highest total GDP as `r list_max_min$GDP$max$GDP[1]`. `r list_max_min$GDP$min$indicator[1]`has the lowest total GDP as `r list_max_min$GDP$min$GDP[1]`. The average total GDP is `r list_max_min$GDP$avg`

3. `r list_max_min$GDP.1$max$indicator[1]` has the highest total GDP as `r list_max_min$GDP.1$max$GDP[1]`. `r list_max_min$GDP.1$min$indicator[1]`has the lowest total GDP as `r list_max_min$GDP.1$min$GDP[1]`. The average total GDP is `r list_max_min$GDP.1$avg`. 

4. `r list_max_min$GDP.per.km2$max$indicator[1]` has the highest GDP per square kilometer as `r list_max_min$GDP.per.km2$max$GDP.per.km2[1]`. `r list_max_min$GDP.per.km2$min$indicator[1]`has the lowest GDP per square kilometer as `r list_max_min$GDP.per.km2$min$GDP.per.km2[1]`. The average GDP per square kilometer is `r list_max_min$GDP.per.km2$avg`. 

5. `r list_max_min$land.area..sq.km$max$indicator[1]` has the largest land area as `r list_max_min$land.area..sq.km$max$land.area..sq.km[1]` square kilometer. `r list_max_min$land.area..sq.km$min$indicator[1]`has the smallest land area as `r list_max_min$land.area..sq.km$min$land.area..sq.km[1]` square kilometer. The average land area is `r list_max_min$land.area..sq.km$avg` square kilometer. 

6. `r list_max_min$population.density$max$indicator[1]` has the largest population density as `r list_max_min$population.density$max$population.density[1]`. `r list_max_min$population.density$min$indicator[1]`has the lowest population density as `r list_max_min$population.density$min$population.density[1]`. The average population density is `r list_max_min$population.density$avg`. 

7. `r list_max_min$total.foreign.born.population$max$indicator[1]` has the largest total foreign born population as `r list_max_min$total.foreign.born.population$max$total.foreign.born.population[1]`. 
`r list_max_min$total.foreign.born.population$min$indicator[1]`has the lowest total foreign born population as `r list_max_min$total.foreign.born.population$min$total.foreign.born.population[1]`. The average foreign born population in all countries analyzed is `r list_max_min$total.foreign.born.population$avg`. 

8. `r list_max_min$X..foreign.born.population$max$indicator[1]` has the largest percentage of foreign born population as `r list_max_min$X..foreign.born.population$max$X..foreign.born.population[1]`. 
`r list_max_min$X..foreign.born.population$min$indicator[1]`has the lowest percentage of foreign born population as `r list_max_min$X..foreign.born.population$min$X..foreign.born.population[1]`. The average percentage of foreign born population in all countries analyzed is `r list_max_min$X..foreign.born.population$avg`. 

9. `r list_max_min$population.living.abroad..diaspora$max$indicator[1]` has the largest population living abroad whose origin lies in a separate geographic locale as `r list_max_min$population.living.abroad..diaspora$max$population.living.abroad..diaspora[1]`. 
`r list_max_min$population.living.abroad..diaspora$min$indicator[1]`has the smallest population living abroad whose origin lies in a separate geographic locale as `r list_max_min$population.living.abroad..diaspora$min$population.living.abroad..diaspora[1]`. The average population living abroad whose origin lies in a separate geographic locale in all countries analyzed is `r list_max_min$population.living.abroad..diaspora$avg`. 

10. `r list_max_min$population.living.abroad$max$indicator[1]` has the largest population living abroad as `r list_max_min$population.living.abroad$max$population.living.abroad[1]`. 
`r list_max_min$population.living.abroad$min$indicator[1]`has the smallest population living abroad as `r list_max_min$population.living.abroad$min$population.living.abroad[1]`. The average population living abroad in all countries analyzed is `r list_max_min$population.living.abroad$avg`. 

11. `r list_max_min$happy.planet.index$max$indicator[1]` has the highest happy planet index as `r list_max_min$happy.planet.index$max$happy.planet.index[1]`, which means they are doing the best at achieving long, happy, sustainable lives in these 20 countries that have evaluated. 
`r list_max_min$happy.planet.index$min$indicator[1]`has the smallest happy planet index as `r list_max_min$happy.planet.index$min$happy.planet.index[1]`, which means they did not do well in achieving long, happy, sustainable lives. The average happy planet index in all countries analyzed is `r list_max_min$happy.planet.index$avg`. 

11. `r list_max_min$world.happiness.report.score$max$indicator[1]` has the highest world happiness report score as `r list_max_min$world.happiness.report.score$max$world.happiness.report.score[1]`. 
`r list_max_min$world.happiness.report.score$min$indicator[1]`has the lowest world happiness report score as `r list_max_min$world.happiness.report.score$min$world.happiness.report.score[1]`. The average world happiness report score in all countries analyzed is `r list_max_min$world.happiness.report.score$avg`. 

12. `r list_max_min$human.development.index$max$indicator[1]` has the highest human development index as `r list_max_min$human.development.index$max$human.development.index[1]`. 
`r list_max_min$human.development.index$min$indicator[1]`has the lowest human development index as `r list_max_min$human.development.index$min$human.development.index[1]`. The average human development index in all countries analyzed is `r list_max_min$human.development.index$avg`. 

13. `r list_max_min$health.expenditure$max$indicator[1]` has the highest health expenditure as `r list_max_min$health.expenditure$max$health.expenditure[1]`. 
`r list_max_min$health.expenditure$min$indicator[1]`has the lowest health expenditure as `r list_max_min$health.expenditure$min$health.expenditure[1]`. The average health expenditure in all countries analyzed is `r list_max_min$health.expenditure$avg`. 

14. `r list_max_min$education.expenditure$max$indicator[1]` has the highest health expenditure as `r list_max_min$education.expenditure$max$education.expenditure[1]`. 
`r list_max_min$education.expenditure$min$indicator[1]`has the lowest health expenditure as `r list_max_min$education.expenditure$min$education.expenditure[1]`. The average health expenditure in all countries analyzed is `r list_max_min$education.expenditure$avg`. 

#Chart 1: Foreign immigrants analysis
For the first graph, we investigated the relationship between the *GDP* and the *foreign immigrants* in the 76 countries. The country name could be shown by clicking on the responding dots. 

```{r message=FALSE}
dataframe_choice <- read.csv(
  "data/WDVP Datasets - small countries are beautiful.csv",
  stringsAsFactors = F, na.strings = "-")

chart_one <- gdp_area_vs_foreign_born(dataframe_choice)
chart_one
```

#Chart 2: Health expenditure analysis
For the second chart, we analyzed the relationship between the *health expenditure* and the *human development index* for 2017 in the 76 countries. The country name and the value of human development index, the health expenditure would be shown by clicking on the bar interested. 

```{r}
data_set <- read.csv("data/WDVP Datasets - small countries are beautiful.csv", stringsAsFactors = FALSE, na.strings = "-")

chart_two <- get_second_chart(data_set)
chart_two

```